Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-06-04 performance_comparison.tex
[mg] sec 5 review

\subsection{Simulations with noise realization}
Finally, we provide an empirical validation of the closed-loop robustified planning by simulating the evolution of the controlled vehicle with random initial conditions and including noise realizations. The random values for the initial state and the noise follow Gaussian distributions with covariance matrices $\bP_0$ and $\bQ$, respectively, as introduced in~\eqref{eq:dP}. This analysis cannot be performed for the open-loop approach, as it does not compute a stabilizing controller---resulting in trajectories that would significantly deviate from the track limits beyond the prediction horizon. For visual clarity, the comparison is limited to trajectories with the robustified TLC, but analogous considerations apply to the robustified FLC as well.

The left panel of Figure~\ref{fig:traj_strings} shows random evolutions (red lines) for an LQR-controlled vehicle stabilized to follow the nominal optimal trajectory (black line). No robust constraints are introduced, and the controller implements the feedback policy from step 2 of Subsection~\ref{sec:LQR}. The right panel, instead, shows the random evolutions (red lines) for the robustified LQR-based controller obtained in the step 3 of the closed-loop approach described in Subsection~\ref{sec:CLrobustified}. The corresponding robustified mean trajectory is shown in black.
The comparison between the panels shows that the robustified controller is significantly more effective at satisfying the TLC. Indeed, even the most lateral trajectories remain within the track boundaries.

>>>>

\subsection{Simulations with noise realization}
Finally, we provide an empirical validation of the closed-loop robustified planning by simulating the evolution of the controlled vehicle with random initial conditions and including noise realizations. The random values for the initial state and the noise follow Gaussian distributions with covariance matrices $\bP_0$ and $\bQ$, respectively, as introduced in~\eqref{eq:dP}. This analysis cannot be performed for the open-loop approach, as it does not compute a stabilizing controller---resulting in trajectories that would significantly deviate from the track limits beyond the prediction horizon. 
%For visual clarity, the comparison is limited to trajectories with the robustified TLC, but analogous considerations apply to the robustified FLC as well.

The left panel of Figure~\ref{fig:traj_strings} shows random evolutions (red lines) for an LQR-controlled vehicle stabilized to follow the nominal optimal trajectory (black line). No robust constraints are introduced, and the controller implements the feedback policy from step 2 of Subsection~\ref{sec:LQR}. The right panel, instead, shows the random evolutions (red lines) for the robustified LQR-based controller obtained in the step 3 of the closed-loop approach described in Subsection~\ref{sec:CLrobustified}. The corresponding robustified mean trajectory is shown in black.
The comparison between the panels shows that the robustified controller is significantly more effective at satisfying the TLC, resulting in safer and more reliable trajectory tracking.
